\textcolor{red}{Building Suitable Datasets for Soft Computing and Machine Learning Techniques from Meteorological Data Integration: A case study for predicting significant wave height and flux of energy}

### 2020-09-29 latex_manuscript/MDPI/2_energies_special_issue/template.tex
Cambios para Special Issue Energies

		\textcolor{red}{VOY POR AQUI!!!!!!}

		The information to create these datasets can be obtained from meteorological observations, but such information may be available in a inappropriate format and even contain missing values or measurements. Consequently, it is usually required to perform pre-processing tasks for improving the quality of the data, such as the replacement of missing values, outlier detection or data normalisation, among others. Furthermore, if more than one source of information is used to achieve a better characterisation of the problem under study \cite{JOHANSSON2015143, FERNANDEZ201544, Adams2010}, then a data integration process, denominated as the matching process in this document, has to be carried out by the researchers to manually create the datasets with the needed information. Moreover, depending on the subject and the ML technique to be applied, or even if the researcher considers other factors in order to improve the results or have more in-depth conclusions, the datasets would have to be updated afterwards. In summary, many important details and different intermediate steps have to be considered when creating suitable datasets for ML techniques, resulting in an extremely tedious task.

		The main purpose of this paper is to present a new open source tool for the creation of datasets integrated by meteorological variables from two sources of information. Given that the tool provides an user-friendly graphical interface, no knowledge in programming languages is needed, and it also prevents researchers from performing the mentioned tedious work and greatly simplify all the steps involved in it, avoiding possible errors in the intermediate steps. The meteorological data used by the tool come from two well-known sources of information: the \textit{National Oceanic and Atmospheric Administration} (NOAA) \textit{National Data Buoy Center} (NDBC) \cite{NOAA} and the \textit{National Centers for Environmental Prediction} (NCEP)/\textit{National Center for Atmospheric Research} (NCAR) \textit{Reanalysis Project} (NNRP or R1) \cite{Kalnay1996, Kistler2001}. The software tool presented in this work is named SPAMDA (Software for Pre-processing and Analysis of Meteorological DAta to build datasets). As SPAMDA performs all this data processing, it reduces the time involving these tasks and allows the researchers focus on the study of the meteorological aspects of the observations. The datasets obtained are ready to be used as input for ML techniques in prediction tasks (classification or regression), although the researchers can use them for other purposes. These datasets contain one or more meteorological variables as inputs and one variable as target (variable to be predicted). The format of the generated datasets will be \textit{Attribute-Relation File Format} (ARFF) \cite{WEKA_ARFF}, which is the one used by WEKA. Besides, the datasets can also be generated in \textit{Comma-Separated Values} (CSV) format, enabling the researchers to use others tools.

		Up to now, and to the best of our knowledge, this is the first software tool addressing the problem previously discussed, integrating meteorological data from NDBC and NNRP. The novelties and functionalities that SPAMDA offers to the researchers will be detailed in Section \ref{sec:SPAMDA}, although some of them are briefly summarised below \textcolor{red}{Esto hay que revisarlo}:
		\begin{itemize}
			\item The generation of datasets becomes a very easy and customisable task, by means of the selection of different input parameters, such as predictive and objective variables, classification and regression ML techniques, output discretisation or prediction horizon, among others.
			\item It makes the researcher focus on environmental modelling, without having to worry about mechanical tasks, avoiding laborious pre-processing procedures that imply a lot of time and effort. \textcolor{red}{Decir que permite un estudio previo o sondeo antes de hacer estudios más exhaustivos}
			\item It manages the extensive casuistry of data integration which can lead to incomplete datasets.
			\item It avoids possible researcher errors in the intermediate steps of the process, such as time and geographical coordinates conversion or missing values handling (dates or measurements not recorded), among others.
			\item It provides information about the quality and quantity of the data.
			\item It includes different pre-processing tasks, such as normalisation and missing data recovery.\textcolor{red}{Hay que quitarle importancia al tema del preprocesamiento, para que no nos comparen con eso.}
			\item It facilitates data management and well-organised storage of the datasets.
			\item The created datasets can be easily used by ML tools.
			\item Its modular design allows the implementation of new modules for managing meteorological data from others sources, benefiting future renewable energy and environmental research.
			\item It includes a user-friendly GUI, facilitating and greatly simplifying data management, and it is integrated with the Explorer environment of WEKA.
			\item It is multi-platform, and it can be used on any computer with Java regardless of the operating system.
		\end{itemize}

@@

				\textcolor{red}{Aquí en esta subsección hay que intentar darle poca importancia respecto a que el software no se centra en los filtros de preprocesamiento}

@@

							\item \textit{'N' (one per each reanalysis node)}: As many final datasets as the number of nearest $N$ reanalysis nodes configured by the researcher will be created. Therefore, each final dataset will contain the value of each reanalysis variable used of the nearest corresponding reanalysis node, along with the selected attributes of the intermediate or pre-processed dataset used.

@@

			\textcolor{red}{Quizas deberiamos poner algun parrafo mas sobre las conclusiones de la experimentacion, mirar el paper mio de ``Significant wave height and energy flux range forecast with machine learning classifiers'' por si sacar algo. Y quizas deberiamos hacer la experimentacion tambien con el flujo de energia en forma de regresion, ya que el special issue se titula ``Soft Computing Techniques in Energy System''. ¿Esta el dataset en el repositorio?}

>>>>

		The information to create these datasets \textcolor{red}{related with MRE} can be obtained from meteorological observations, but such information may be available in a inappropriate format and even contain missing values or measurements. Consequently, it is usually required to perform pre-processing tasks for improving the quality of the data, such as the replacement of missing values, outlier detection or data normalisation, among others. Furthermore, if more than one source of information is used to achieve a better characterisation of the problem under study \cite{JOHANSSON2015143, FERNANDEZ201544, Adams2010}, then a data integration process, denominated as the matching process in this document and \textcolor{red}{in which the main feature of the tool presented in this work is focused}, has to be carried out by the researchers to manually create the datasets with the needed information. Moreover, depending on the subject and the \textcolor{red}{SC and }ML technique to be applied, or even if the researcher considers other factors in order to improve the results or have more in-depth conclusions, the datasets would have to be updated afterwards. In summary, many important details and different intermediate steps have to be considered when creating suitable datasets, \textcolor{red}{especially when there is data integration}, resulting in an extremely tedious task.

		The main purpose of this paper is to present a new open source tool for the creation of datasets integrated by meteorological variables from two sources of information. Given that the tool provides an user-friendly graphical interface, no knowledge in programming languages is needed, and it also prevents researchers from performing the mentioned tedious work and greatly simplify all the steps involved in it, avoiding possible errors in the intermediate steps\textcolor{red}{, at least as a preliminary study of certain areas}. The meteorological data used by the tool come from two well-known sources of information: the \textit{National Oceanic and Atmospheric Administration} (NOAA) \textit{National Data Buoy Center} (NDBC) \cite{NOAA} and the \textit{National Centers for Environmental Prediction} (NCEP)/\textit{National Center for Atmospheric Research} (NCAR) \textit{Reanalysis Project} (NNRP or R1) \cite{Kalnay1996, Kistler2001}. The software tool presented in this work is named SPAMDA (Software for Pre-processing and Analysis of Meteorological DAta to build datasets). As SPAMDA performs all this data processing, it reduces the time involving these tasks and allows the researchers focus on the study of the meteorological aspects of the observations. The datasets obtained are ready to be used as input for \textcolor{red}{SC and }ML techniques in prediction tasks (classification or regression), although the researchers can use them for other purposes. These datasets contain one or more meteorological variables as inputs and one variable as target (variable to be predicted). The format of the generated datasets will be \textit{Attribute-Relation File Format} (ARFF) \cite{WEKA_ARFF}, which is the one used by WEKA. Besides, the datasets can also be generated in \textit{Comma-Separated Values} (CSV) format, enabling the researchers to use others tools.

		Up to now, and to the best of our knowledge, this is the first software tool \textcolor{red}{with GUI (Graphical User Interface) }addressing the problem previously discussed, integrating meteorological data from NDBC and NNRP \textcolor{red}{and the casuistry that it entails}. \textcolor{blue}{(desde ''Up to now... hasta ...entails lo quitaría)} The novelties and functionalities that SPAMDA offers to the researchers will be detailed in Section \ref{sec:SPAMDA}, although some of them are briefly summarised below \textcolor{red}{Esto hay que revisarlo}:
		\begin{itemize}
			%\item The generation of datasets becomes a very easy and customisable task, by means of the selection of different input parameters, such as predictive and objective variables, classification and regression ML techniques, output discretisation or prediction horizon, among others.
			\item The generation of datasets \textcolor{red}{with SPAMDA} becomes a very easy and customisable task by means of the selection of different input parameters, such as predictive and objective variables, classification and regression, output discretisation \textcolor{red}{(even for ordinal regression)} or prediction horizon, among others.
			\item The created datasets can be easily used by \textcolor{red}{SC and }ML tools.
			\item It provides information about the quality and quantity of the data.
			\item It makes the researcher focus on environmental modelling, without having to worry about mechanical tasks, avoiding laborious pre-processing procedures \textcolor{red}{as scripts}, that imply a lot of time and effort, \textcolor{red}{at least in early stages of the research}. \textcolor{red}{Por tanto, esta herramienta podría ser tambíen de utilidad en estudios previos realizados sobre diferentes zonas oceánicas y costeras where some kind of environmental prediction is needed.}
			\item It avoids possible researcher errors in the intermediate steps of the process, such as time and geographical coordinates conversion or missing values handling (dates or measurements not recorded), \textcolor{red}{different data collection times, }among others.
			\item It manages the extensive casuistry of data integration which can lead to incomplete datasets.
			\item \textcolor{red}{Possibility of using one or more reanalysis points close to the study location.}
			\item It includes different pre-processing tasks, such as normalisation and missing data recovery, \textcolor{red}{aunque esa no es la característica en la que se centra la herramienta, sino en el preprocesamiento y cauistica generada por la integración de los datos provenientes del NDBC y NNRP. Un preprocesamiento mucho más amplio se puede realizar posteriormente con otras herramientas, incluso con el propio módulo de Weka que se integra en SPAMDA.}
			\item It facilitates data management and well-organised storage of the datasets.
			\item \textcolor{red}{Providing the source code to the scientific community and }its modular design allows the implementation of new modules for managing meteorological data from others sources, benefiting future renewable energy and environmental research.
			\item It includes a user-friendly GUI, facilitating and greatly simplifying data management, and it is integrated with the Explorer environment of WEKA.
			\item It is multi-platform, and it can be used on any computer with Java regardless of the operating system.
		\end{itemize}

@@

				\textcolor{red}{Aquí en esta subsección hay que intentar darle poca importancia respecto a que el software no se centra en los filtros de preprocesamiento, como se indico al final de la introduccion}

@@

							\item \textit{'N' (one per each reanalysis node)}: As many final datasets as the number of nearest $N$ reanalysis nodes configured by the researcher will be created. Therefore, each final dataset will contain the value of each reanalysis variable used of the nearest corresponding reanalysis node, along with the selected attributes of the intermediate or pre-processed dataset used. \textcolor{red}{No se si deberiamos resaltar un poco esta funcionalidad, porque no se explota mucho en el paper creo, o al menos ni lo leen o ni la ven.}

@@

			\textcolor{red}{Quizas deberiamos poner algun parrafo mas sobre las conclusiones de la experimentacion, mirar el paper mio de ``Significant wave height and energy flux range forecast with machine learning classifiers'' por si sacar algo. Y quizas deberiamos hacer la experimentacion tambien con el flujo de energia en forma de regresion, ya que el special issue se titula ``Soft Computing Techniques in Energy System''. ¿Esta el dataset en el repositorio?. Esto es lo que nos llevaria mas tiempo, el resto del paper no debemos tocarlo mucho mas de lo que tenemos anotado.}
